New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-09-21 paper/paper.Rmd
fixed few sentences

However, it can be hard to alter the behaviour of the control objects such as setting the 1D slider on a different scale  (Slider increments add 10 points into the slice rather than increasing the slice height by 0.1 for example). \textcolor{red}{but this is no longer true if you replace it with animate??}
\textcolor{red}{Alex, is this still true with the controls you are using now?}

\textcolor{red}{Ursula: this comment about slider scale seems to specific, can we have a more general comment about difficulties, e.g. I remember some issues with the color mapping? Also there seem to be a lot of loops needed? Can you explain what the locator pane is?}

The examples presented in the penguins’ notebooks all use our primary new function, `SliceDynamic`. This function typically accepts grouped data in the form of a matrix where the second last column details the name of the group and the last column details the group index \textcolor{red}{(which can be one if there is only one group)}. After specifying the initial slice thickness and the slice range, the user is presented with an interactive display in which the control objects appear on the left and the slice visulisation appears on the right. The user can change the orientation of the slice via the locator pane, which changes the projection matrix;  a slider controls the slice thickness; and there is an input field, which changes the slice centre. The user can also change the appearance of the plot by zooming into the center or changing the point size with sliders provided.\textcolor{red}{this zoom doesn't work very well} The projected data can be displayed to contrast it with the slice by ticking a box. The explicit projection matrix can also be displayed via another checkbox. This is especially useful when we wish to import a projection that was identified as interesting in the manual exploration later, as shown in the applications below.

>>>>

The most important inbuilt Mathematica function for our purpose is the locator pane. This creates a region on the screen where the position of the mouse is converted to input for the graphics functions, enabling the manual navigation of the tour.

\textcolor{red}{To Ursula:I removed the comment on the slider. There are no problems with color mapping. What do you mean by:" Also there seem to be a lot of loops needed?"? as far as I can tell the code does not use any loop. Is my explanantion of the locator pane enough? Please modify as you see fit and finish up this section.}

The examples presented in the penguins’ notebooks all use our primary new function, `SliceDynamic`. This function typically accepts grouped data in the form of a matrix where the second last column details the name of the group and the last column details the group index \textcolor{red}{(which can be one if there is only one group)}. After specifying the initial slice thickness and the slice range, the user is presented with an interactive display in which the control objects appear on the left and the slice visulisation appears on the right. The user can change the orientation of the slice via the locator pane, which changes the projection matrix;  a slider controls the slice thickness; and there is an input field, which changes the slice centre. The user can also change the appearance of the plot by zooming into the center or changing the point size with sliders provided. \textcolor{red}{It is worth noting that this zoom works best with data that has been centred and scaled.} The projected data can be displayed to contrast it with the slice by ticking a box. The explicit projection matrix can also be displayed via another checkbox. This is especially useful when we wish to import a projection that was identified as interesting in the manual exploration later, as shown in the applications below.

### 2022-09-21 paper/paper.tex
fixed few sentences

The problem with \textcolor{red}{the} new simple method is that it is
not faithful to the precise values for \(V_m\) because the
orthonormalisation will change them.
\textcolor{red}{Even though these changes are for the most part imperceptible, one may wits to remove them and}
there are numerous ways that this can be enforced, and details are given
in the Appendix.
\textcolor{red}{While they all enforce the same position for the selected variable, they differ in how the remaining variables are adjusted during orthonormalisation.}

@@

However, it can be hard to alter the behaviour of the control objects
such as setting the 1D slider on a different scale (Slider increments
add 10 points into the slice rather than increasing the slice height by
0.1 for example).
\textcolor{red}{but this is no longer true if you replace it with animate??}
\textcolor{red}{Alex, is this still true with the controls you are using now?}

\textcolor{red}{Ursula: this comment about slider scale seems to specific, can we have a more general comment about difficulties, e.g. I remember some issues with the color mapping? Also there seem to be a lot of loops needed? Can you explain what the locator pane is?}

The examples presented in the penguins' notebooks all use our primary
new function, \texttt{SliceDynamic}. This function typically accepts
grouped data in the form of a matrix where the second last column
details the name of the group and the last column details the group
index \textcolor{red}{(which can be one if there is only one group)}.
After specifying the initial slice thickness and the slice range, the
user is presented with an interactive display in which the control
objects appear on the left and the slice visulisation appears on the
right. The user can change the orientation of the slice via the locator
pane, which changes the projection matrix; a slider controls the slice
thickness; and there is an input field, which changes the slice centre.
The user can also change the appearance of the plot by zooming into the
center or changing the point size with sliders
provided.\textcolor{red}{this zoom doesn't work very well} The projected
data can be displayed to contrast it with the slice by ticking a box.
The explicit projection matrix can also be displayed via another
checkbox. This is especially useful when we wish to import a projection
that was identified as interesting in the manual exploration later, as
shown in the applications below.

>>>>

The problem with \textcolor{red}{the} new simple method is that it is
not faithful to the precise values for \(V_m\) because the
orthonormalisation will change them.
\textcolor{red}{Even though these changes are for the most part imperceptible, one may wish to avoid them and}
there are numerous ways that this can be enforced, a few are detailed in
the Appendix.
\textcolor{red}{While they all enforce the same position for the selected variable, they differ in how the remaining variables are adjusted during orthonormalisation.}

@@

The most important inbuilt Mathematica function for our purpose is the
locator pane. This creates a region on the screen where the position of
the mouse is converted to input for the graphics functions, enabling the
manual navigation of the tour.

\textcolor{red}{To Ursula:I removed the comment on the slider. There are no problems with color mapping. What do you mean by:" Also there seem to be a lot of loops needed?"? as far as I can tell the code does not use any loop. Is my explanantion of the locator pane enough? Please modify as you see fit and finish up this section.}

The examples presented in the penguins' notebooks all use our primary
new function, \texttt{SliceDynamic}. This function typically accepts
grouped data in the form of a matrix where the second last column
details the name of the group and the last column details the group
index \textcolor{red}{(which can be one if there is only one group)}.
After specifying the initial slice thickness and the slice range, the
user is presented with an interactive display in which the control
objects appear on the left and the slice visulisation appears on the
right. The user can change the orientation of the slice via the locator
pane, which changes the projection matrix; a slider controls the slice
thickness; and there is an input field, which changes the slice centre.
The user can also change the appearance of the plot by zooming into the
center or changing the point size with sliders provided.
\textcolor{red}{It is worth noting that this zoom works best with data that has been centred and scaled.}
The projected data can be displayed to contrast it with the slice by
ticking a box. The explicit projection matrix can also be displayed via
another checkbox. This is especially useful when we wish to import a
projection that was identified as interesting in the manual exploration
later, as shown in the applications below.
